---
output:
  word_document: default
  html_document: default
---
## Phase 1

### Mitchell Poll

Libraries.  
```{r, message=FALSE, echo=FALSE}
library(tidyverse)
library(tidymodels)
library(mice)
library(vip)
library(esquisse)
library(skimr)
library(gridExtra)
library(GGally)
library(corrplot)
```

Read in Dataset.  
```{r, message=FALSE, echo=FALSE}
ames=read.csv("ames_student.csv")
#summary(ames)
#str(ames)
#skim(ames)
```

```{r, message=FALSE, echo=FALSE}
ames_clean = ames %>%
  mutate_if(is.character,as_factor) %>%
  mutate(Mo_Sold=as_factor(Mo_Sold)) %>%
  mutate(Year_Sold=as_factor(Year_Sold)) %>%
  mutate(Full_Bath=as_factor(Full_Bath)) %>%
  mutate(Half_Bath=as_factor(Half_Bath)) %>%
  mutate(Bedroom_AbvGr=as_factor(Bedroom_AbvGr)) %>%
  mutate(Kitchen_AbvGr=as_factor(Kitchen_AbvGr)) %>%
  mutate(Bsmt_Full_Bath=as_factor(Bsmt_Full_Bath)) %>%
  mutate(Bsmt_Half_Bath=as_factor(Bsmt_Half_Bath)) %>%
  mutate(TotRms_AbvGrd=as_factor(TotRms_AbvGrd))
```

Split Data into train and test.  
```{r}
set.seed(1234)
ames_split=initial_split(ames_clean, prop=0.7, strata=Above_Median)
train=training(ames_split)
test=testing(ames_split)
```

Correlation. Got code from https://towardsdatascience.com/how-to-create-a-correlation-matrix-with-too-many-variables-309cc0c0a57   
```{r, message=FALSE, echo=FALSE}
# corr_simple = function(data=train, sig=.45) {
#   df_cor = train %>% mutate_if(is.character, as_factor)
#   df_cor = df_cor %>% mutate_if(is.factor, as.numeric)
#   
#   corr = cor(df_cor)
#   corr[lower.tri(corr, diag=TRUE)] = NA
#   corr[corr==1] =NA
#   
#   corr = as.data.frame(as.table(corr))
#   corr = na.omit(corr)
#   
#   corr = subset(corr, abs(Freq) > sig)
#   corr = corr[order(-abs(corr$Freq)),]
#   
#   print(corr)
#   
#   mtx_corr = reshape2::acast(corr, Var1~Var2, value.var="Freq")
#   
#   corrplot(mtx_corr, is.corr=FALSE, tl.col="black", na.label=" ")
# }
# 
# corr_simple()
```

It appears that Year_Built, Year_Remod_Add, Exter_Qual, Gr_Liv_Area, Full_Bath, Fireplaces, Garage_Type, Garage_Cars, and Garage_Area are the most highly correlated to Above_Median. I borrowed code so that I didn't have to plot out all 81 variables.    

Visualization.  
```{r, message=FALSE, echo=FALSE}
# p1=ggplot(train, aes(Above_Median, Year_Built)) + geom_boxplot()
# p2=ggplot(train, aes(Above_Median, Year_Remod_Add)) + geom_boxplot()
# p3=ggplot(train, aes(Exter_Qual, fill=Above_Median)) + geom_bar(position="fill") + theme(axis.text.x=element_text(angle=90, vjust=.5, hjust=1))
# p4=ggplot(train, aes(Above_Median, Gr_Liv_Area)) + geom_boxplot()
# p5=ggplot(train, aes(Above_Median, Full_Bath)) + geom_boxplot()
# p6=ggplot(train, aes(Above_Median, Fireplaces)) + geom_boxplot()
# p7=ggplot(train, aes(Garage_Type, fill=Above_Median)) + geom_bar(position="fill") + theme(axis.text.x=element_text(angle=90, vjust=.5, hjust=1))
# p8=ggplot(train, aes(Above_Median, Garage_Cars)) + geom_boxplot()
# p9=ggplot(train, aes(Above_Median, Garage_Area)) + geom_boxplot()
# ```
# 
# ```{r, message=FALSE}
# grid.arrange(p1, p2, p4, p5)
# grid.arrange(p6, p8, p9)
# grid.arrange(p3)
# grid.arrange(p7)
```

Visualization: factor   
```{r, fig.width=15, fig.height=15}
# ggplot(train, aes(Above_Median, Year_Remod_Add)) + geom_boxplot()
# ggplot(train, aes(Exter_Qual, fill=Above_Median)) + geom_bar(position="fill") + theme(axis.text.x=element_text(angle=90, vjust=.5, hjust=1))

my_theme=theme(axis.text.x=element_text(angle=90, vjust=.5, hjust=1, size=20), axis.title=element_text(size=30))

#Factors

p1=ggplot(train, aes(MS_SubClass, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p2=ggplot(train, aes(MS_Zoning, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p3=ggplot(train, aes(Street, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p4=ggplot(train, aes(Alley, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p5=ggplot(train, aes(Lot_Shape, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p6=ggplot(train, aes(Land_Contour, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p7=ggplot(train, aes(Utilities, fill=Above_Median)) + geom_bar(position="fill") + my_theme
#ggplot(train, aes(Lot_Config, fill=Above_Median)) + geom_bar(position="fill") + theme(axis.text.x=element_text(angle=90, vjust=.5, hjust=1))
p8=ggplot(train, aes(Land_Slope, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p9=ggplot(train, aes(Neighborhood, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p10=ggplot(train, aes(Condition_1, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p11=ggplot(train, aes(Condition_2, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p12=ggplot(train, aes(Bldg_Type, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p13=ggplot(train, aes(House_Style, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p14=ggplot(train, aes(Overall_Qual, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p15=ggplot(train, aes(Overall_Cond, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p16=ggplot(train, aes(Roof_Style, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p17=ggplot(train, aes(Roof_Matl, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p18=ggplot(train, aes(Exterior_1st, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p19=ggplot(train, aes(Exterior_2nd, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p20=ggplot(train, aes(Mas_Vnr_Type, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p21=ggplot(train, aes(Exter_Qual, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p22=ggplot(train, aes(Exter_Cond, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p23=ggplot(train, aes(Foundation, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p24=ggplot(train, aes(Bsmt_Qual, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p25=ggplot(train, aes(Bsmt_Cond, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p26=ggplot(train, aes(Bsmt_Exposure, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p27=ggplot(train, aes(BsmtFin_Type_1, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p28=ggplot(train, aes(BsmtFin_Type_2, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p29=ggplot(train, aes(Heating, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p30=ggplot(train, aes(Heating_QC, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p31=ggplot(train, aes(Central_Air, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p32=ggplot(train, aes(Electrical, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p33=ggplot(train, aes(Kitchen_Qual, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p34=ggplot(train, aes(Functional, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p35=ggplot(train, aes(Fireplace_Qu, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p36=ggplot(train, aes(Garage_Type, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p37=ggplot(train, aes(Garage_Finish, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p38=ggplot(train, aes(Garage_Qual, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p39=ggplot(train, aes(Garage_Cond, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p40=ggplot(train, aes(Paved_Drive, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p41=ggplot(train, aes(Pool_QC, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p42=ggplot(train, aes(Fence, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p43=ggplot(train, aes(Misc_Feature, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p44=ggplot(train, aes(Sale_Type, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p45=ggplot(train, aes(Sale_Condition, fill=Above_Median)) + geom_bar(position="fill") + my_theme
#ggplot(train, aes(Mo_Sold, fill=Above_Median)) + geom_bar(position="fill") + theme(axis.text.x=element_text(angle=90, vjust=.5, hjust=1))
#ggplot(train, aes(Year_Sold, fill=Above_Median)) + geom_bar(position="fill") + theme(axis.text.x=element_text(angle=90, vjust=.5, hjust=1))
p46=ggplot(train, aes(Full_Bath, fill=Above_Median)) + geom_bar(position="fill") + my_theme
#ggplot(train, aes(Half_Bath, fill=Above_Median)) + geom_bar(position="fill") + theme(axis.text.x=element_text(angle=90, vjust=.5, hjust=1))
#ggplot(train, aes(Bedroom_AbvGr, fill=Above_Median)) + geom_bar(position="fill") + theme(axis.text.x=element_text(angle=90, vjust=.5, hjust=1))
p47=ggplot(train, aes(Kitchen_AbvGr, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p48=ggplot(train, aes(Bsmt_Full_Bath, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p49=ggplot(train, aes(Bsmt_Half_Bath, fill=Above_Median)) + geom_bar(position="fill") + my_theme
p50=ggplot(train, aes(TotRms_AbvGrd, fill=Above_Median)) + geom_bar(position="fill") + my_theme

p1
p2
p9
grid.arrange(p3,p4,p5,p6)
grid.arrange(p7,p8,p10)
grid.arrange(p11,p12,p13,p14)
grid.arrange(p15,p16,p17,p18)
grid.arrange(p19,p20,p21,p22)
grid.arrange(p23,p24,p25,p26)
grid.arrange(p27,p28,p29,p30)
grid.arrange(p31,p32,p33,p34)
grid.arrange(p35,p36,p37,p38)
grid.arrange(p39,p40,p41,p42)
grid.arrange(p43,p44,p45,p46)
grid.arrange(p47,p48,p49,p50)
```

Of the factor variables I'll use MS-SubClass, MS_Zoning, Street, Alley, Lot_Shape, Land_Contour, Utilities, Land_Slope, Neighborhood, Condition_1, Condition_2, Bldg_Type, House_Style, Overall_Qual, Overall_Cond, Roof_Style, Roof_Matl, Exterior_1st, Exterior_2nd, Mas_Vnr_Type, Exter_Qual, Exter_Cond, Foundation, Bsmt_Qual, Bsmt_Cond, Bsmt_Exposure, BsmtFin_Type_1, BsmtFin_Type_2, Heating, Heating_QC, Central_Air, Electrical, Kitchen_Qual, Functional, Fireplace_Qu, Garage_Type, Garage_Finish, Garage_Qual, Garage_Cond, Paved_Drive, Pool_QC, Fence, Misc_Feature, Sale_Type, Sale_Condition, Full_Bath, Kitchen_AbvGr, Bsmt_Full_Bath, Bsmt_Half_Bath, TotRms_AbvGrd

Visualization: integer  
```{r}
# ggplot(train, aes(Above_Median, Year_Remod_Add)) + geom_boxplot()

#integer
#ggplot(train, aes(Above_Median, Lot_Frontage)) + geom_boxplot()
#ggplot(train, aes(Above_Median, Lot_Area)) + geom_boxplot()
p51=ggplot(train, aes(Above_Median, Year_Built)) + geom_boxplot()
p52=ggplot(train, aes(Above_Median, Year_Remod_Add)) + geom_boxplot()
p53=ggplot(train, aes(Above_Median, Mas_Vnr_Area)) + geom_boxplot()
p54=ggplot(train, aes(Above_Median, BsmtFin_SF_1)) + geom_boxplot()
#ggplot(train, aes(Above_Median, BsmtFin_SF_2)) + geom_boxplot()
p55=ggplot(train, aes(Above_Median, Bsmt_Unf_SF)) + geom_boxplot()
p56=ggplot(train, aes(Above_Median, Total_Bsmt_SF)) + geom_boxplot()
p57=ggplot(train, aes(Above_Median, First_Flr_SF)) + geom_boxplot()
#ggplot(train, aes(Above_Median, Low_Qual_Fin_SF)) + geom_boxplot()
p58=ggplot(train, aes(Above_Median, Gr_Liv_Area)) + geom_boxplot()
p59=ggplot(train, aes(Above_Median, Fireplaces)) + geom_boxplot()
p60=ggplot(train, aes(Above_Median, Garage_Cars)) + geom_boxplot()
p61=ggplot(train, aes(Above_Median, Garage_Area)) + geom_boxplot()
p62=ggplot(train, aes(Above_Median, Wood_Deck_SF)) + geom_boxplot()
p63=ggplot(train, aes(Above_Median, Open_Porch_SF)) + geom_boxplot()
#ggplot(train, aes(Above_Median, Enclosed_Porch)) + geom_boxplot()
#ggplot(train, aes(Above_Median, Three_season_porch)) + geom_boxplot()
#ggplot(train, aes(Above_Median, Screen_Porch)) + geom_boxplot()
#ggplot(train, aes(Above_Median, Pool_Area)) + geom_boxplot()
#ggplot(train, aes(Above_Median, Misc_Val)) + geom_boxplot()
#ggplot(train, aes(Above_Median, Longitude)) + geom_boxplot()
#ggplot(train, aes(Above_Median, Latitude)) + geom_boxplot()

grid.arrange(p51,p52,p53,p54)
grid.arrange(p55,p56,p57,p58)
grid.arrange(p59,p60,p61,p62,p63)
```
Year_Built, Year_Remod_Add, BsmtFin_SF_1, Bsmt_Unf_SF, Total_Bsmt_SF, First_Flr_SF, Gr_Liv_Area, Fireplaces, Garage_Cars, Garage_Area, Wood_Deck_SF, Open_Porch_SF, Mas_Vnr_Area, 








